AUDIOVISUAL ANALYTICS VOCABULARY AND ONTOLOGY (AAVO): INITIAL CORE AND EXAMPLE EXPANSION

### 2017-09-13 latex/article.tex
incorporadas contribs da Cristina
adicionado numero do proj da fapesp

%%-----------------------------------------------EDIT-----------------------------------------------
\title{Audiovisual Analytics Vocabulary and Ontology (AAVO): initial core and example expansion}

@@

\subsection*{\textit{Acknowledgements}}
The authors thank CNPq and FAPESP for the funding received while researching the topic of this article, the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
where we needed directions for investigation.

>>>>

%%-----------------------------------------------EDIT-----------------------------------------------
\title{AUDIOVISUAL ANALYTICS VOCABULARY AND ONTOLOGY (AAVO): INITIAL CORE AND EXAMPLE EXPANSION}

@@

\subsection*{\textit{Acknowledgements}}
The authors thank FAPESP (project 2017/05838-3) for the funding received while researching the topic of this article, the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
where we needed directions for investigation.
